Crop diversification in a game against nature

### 2020-01-22 risk-percption.Rmd
add may to growing season

sim_present <- brick('~/Downloads/b40.20th.track1.1deg.005.cam2.h0.PRECT.185001-200512.nc') %>%
  raster::extract(konya, df = TRUE) %>%
  select(-ID) %>%
  gather(time, rainfall) %>%
  mutate(rainfall = rainfall * 2.628e+9,
         year = rep(1850:2005, each = 12), # add hardcode dates instead of using ncdf time because of date shift with averaging period
         month = rep(1:12, times = 156)) %>%
  select(-time) %>%
  mutate(water_year = if_else(month %in% 10:12, year + 1L, year)) %>% 
  filter(between(water_year, 1932, 2005)) %>%
   filter(!(month %in% c(5:9))) %>%
  group_by(water_year) %>%
  summarise(precip = sum(rainfall))

>>>>

sim_present <- brick('~/Downloads/b40.20th.track1.1deg.005.cam2.h0.PRECT.185001-200512.nc') %>%
  raster::extract(konya, df = TRUE) %>%
  select(-ID) %>%
  gather(time, rainfall) %>%
  mutate(rainfall = rainfall * 2.628e+9,
         year = rep(1850:2005, each = 12), # add hardcode dates instead of using ncdf time because of date shift with averaging period
         month = rep(1:12, times = 156)) %>%
  select(-time) %>%
  mutate(water_year = if_else(month %in% 10:12, year + 1L, year)) %>% 
  filter(between(water_year, 1932, 2005)) %>%
   filter(!(month %in% c(6:9))) %>%
  group_by(water_year) %>%
  summarise(precip = sum(rainfall))
